TODO: title

### 2014-04-21 paper/main.tex
some work

\section{Introduction}
\section{Methodology}
\section{Results}
\section{Conclusions}

>>>>

\section{Introduction}
\section{Methodology}
\section{Results}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../lenskit/target/analysis/RMSE.pdf}
\caption{caption}
\label{fig:rmse}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../lenskit/target/analysis/nDCG.pdf}
\caption{caption}
\label{fig:ndcg}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../lenskit/target/analysis/MAP.pdf}
\caption{caption}
\label{fig:map}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../lenskit/target/analysis/Precision.pdf}
\caption{caption}
\label{fig:precision}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../lenskit/target/analysis/Precision_fallout.pdf}
\caption{caption}
\label{fig:fallout}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../lenskit/target/analysis/TopN_RMSE_seenItems.pdf}
\caption{caption}
\label{fig:topn.rmse.seen}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../lenskit/target/analysis/TopN_RMSE.pdf}
\caption{caption}
\label{fig:topn.rmse}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../lenskit/target/analysis/TopN_Ave_Rat.pdf}
\caption{caption}
\label{fig:topn.avg.rat}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../lenskit/target/analysis/TopN_MeanPopularity.pdf}
\caption{caption}
\label{fig:pop}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../lenskit/target/analysis/diversity.pdf}
\caption{caption}
\label{fig:diversity}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../lenskit/target/analysis/topN_entropy.pdf}
\caption{caption}
\label{fig:spread}
\end{figure}

\section{Conclusions}
